---
title: "<center> CHAD Output Summary </center>"
subtitle: |
  <center> `r format(Sys.time(), '%d %B, %Y')` </center>
author: 
date:
output: html_document
params:
    radius: NA
    base: NA
    pjDays: NA
    socDis: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = FALSE, warning = FALSE, message = FALSE}
# Some global stuff
library(ggplot2)
library(plotly)
library(knitr)
library(kableExtra)

Counties = GetCounties(params$base, params$radius)
Hospitals = GetHospitals(params$base, params$radius)
CountyDT = GetLocalDataTable(Counties)
CovidCounties = subset(CovidConfirmedCases, CountyFIPS %in% Counties$FIPS)
CovidCountiesDeath<-subset(CovidDeaths, CountyFIPS %in% Counties$FIPS)
CountyCovid = CalculateCovid(Counties)
CountyDeaths = CalculateDeaths(Counties)
TotPop = CalculateCounties(Counties)
CovidCaseChng = sum(rev(CovidCounties)[,1] - rev(CovidCounties)[,2])
CovidDeathChng <- sum(rev(CovidCountiesDeath)[,1] - rev(CovidCountiesDeath)[,2])
HospUltz = HospitalIncreases(Counties)
#HospUltz2 = HospitalUtlzChng(Counties)


if (is.null(params$socDis) ){social_dist<-1}
        
        CS      <- "CS"       %in% params$socDis
        CB    <- "CB"     %in% params$socDis
        SD <- "SD"  %in% params$socDis
        
        if (CS & CB & SD){
            social_dist <- 27
        } else if (CS & CB){
            social_dist <- 12
        } else if (CS & SD){
            social_dist <-19
        } else if (SD & CB){
            social_dist <-23
        } else if (CS) {
            social_dist <- 4
        }  else if (CB) {
            social_dist <- 8
        }  else if (SD) {
            social_dist <- 15
        }


```

```{r echo=FALSE}

OverlayDatahosp = PlotOverlay2(params$base, 
                      Counties, 
                      Hospitals, 
                      social_dist, 
                      params$pjDays,
                      "Hospitalizations")

overlayDF7h <- dplyr::filter(OverlayDatahosp, ForecastDate == Sys.Date()+7)
overlayDF14h <- dplyr::filter(OverlayDatahosp, ForecastDate == Sys.Date()+14)
overlayDF30h <- dplyr::filter(OverlayDatahosp, ForecastDate == Sys.Date()+30)

OverlayDatafatal = PlotOverlay2(params$base, 
                      Counties, 
                      Hospitals, 
                      social_dist, 
                      params$pjDays,
                      "Deaths")

overlayDF7f <- dplyr::filter(OverlayDatafatal, ForecastDate == Sys.Date()+7)
overlayDF14f <- dplyr::filter(OverlayDatafatal, ForecastDate == Sys.Date()+14)
overlayDF30f <- dplyr::filter(OverlayDatafatal, ForecastDate == Sys.Date()+30)

```
---





<center>
#  `r params$base` 
</center>

The Air Force COVID-19 Health Assessment Dashboard (CHAD) was developed to provide a centralized location for leadership to receive up-to-date pandemic information specifically tailored to their installation and the surrounding local area. 

This report was generated using a **`r params$radius` mile radius** around **`r params$base`** as the defined local area.




## Current Local Area Info

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

<div class = "row">

<div class = "col-md-5">

Local Population: 

**`r comma(TotPop)`**

Total Cases:

**`r comma(CalculateCovid(Counties))`**

New Cases: 

**`r paste("+",comma(CovidCaseChng))`**

Total Fatalities: 

**`r comma(CalculateDeaths(Counties))`**

New Fatalities: 

**`r paste("+",comma(CovidDeathChng))`**

Estimated Hospital Utilization:

**`r HospUltz`**



</div>

<div class = "col-md-7">

```{r fig.height = 4, fig.width = 5, echo=FALSE, warning = FALSE}
CountyChoro = PlotLocalChoro(Counties, params$base, "County")
CountyChoro
```

</div>
</div>

## Local Area Plots

<br>

### Daily Stats

The charts below display daily values and cumulative values of cases, hospitalizations, and fatalities

<div class = "row">

<div class = "col-md-6">
```{r fig.height = 4, fig.width = 4, echo=FALSE}
DailyChart <- CovidCasesPerDayChart(Counties)
        DailyChart <- dplyr::filter(DailyChart, ForecastDate >= DailyChart$ForecastDate[1] + 35)
        
        plotDaily <- ggplot(DailyChart) + 
            geom_line(aes(x=ForecastDate, y=value, colour = variable), size = 0.5) +
            scale_colour_manual(values=c("Blue", "Red")) +
            xlab('Date') +
            ylab('Number of People') +
            theme_bw() + 
            theme(plot.title = element_text(face = "bold", size = 15, family = "sans"),
                  axis.title = element_text(face = "bold", size = 11, family = "sans"),
                  axis.text.x = element_text(angle = 60, hjust = 1), 
                  axis.line = element_line(color = "black"),
                  legend.position = "top",
                  plot.background = element_blank(),
                  panel.grid.major = element_blank(),
                  panel.grid.minor = element_blank(),
                  panel.border = element_blank()) +
            scale_x_date(date_breaks = "1 week") +
            labs(color='')
        
        plotDaily <- ggplotly(plotDaily)
        plotDaily <- plotDaily %>% layout(legend = list(orientation = "h",   # show entries horizontally
                                          xanchor = "center",  # use center of legend as anchor
                                          x = 0.5,
                                          y = 1.2)) %>% config(displayModeBar = FALSE)
        
        plotDaily = plotDaily %>% layout(xaxis = list(showgrid = T),
                                         yaxis = list(showgrid = T))
plotDaily
```
</div>

<div class = "col-md-6">
```{r fig.height = 4, fig.width = 4, echo=FALSE}
CumulChart <- CovidCasesCumChart(Counties)
        CumulChart <- dplyr::filter(CumulChart, ForecastDate >= CumulChart$ForecastDate[1] + 35)
        
        #Plot for local area cumulative cases
        plotTot <- ggplot(CumulChart,height = 250) + 
            geom_line(aes(x=ForecastDate, y=value, colour = variable), size = 0.5) +
            scale_colour_manual(values=c("Blue", "Red"))+
            xlab('Date') +
            ylab('Number of People') +
            theme_bw() + 
            theme(plot.title = element_text(face = "bold", size = 15, family = "sans"),
                  axis.title = element_text(face = "bold", size = 11, family = "sans"),
                  axis.text.x = element_text(angle = 60, hjust = 1), 
                  axis.line = element_line(color = "black"),
                  plot.background = element_blank(),
                  panel.grid.major = element_blank(),
                  panel.grid.minor = element_blank(),
                  panel.border = element_blank(),
                  legend.position = c(0, 1),) +
            scale_x_date(date_breaks = "1 week")
        
        plotTot <- ggplotly(plotTot)
        plotTot <- plotTot %>% layout(legend = list(orientation = "h",   # show entries horizontally
                                          xanchor = "center",  # use center of legend as anchor
                                          x = 0.5,
                                          y = 1.2)) %>% config(displayModeBar = FALSE)
        
        plotTot = plotTot %>% layout(xaxis = list(showgrid = T),
                                     yaxis = list(showgrid = T))
plotTot
```
</div>

</div>



### Local Projections

This section will display the projections from the IHME model and the CHIME inspired model on the same graph for daily hospitalizations and cumulative fatalities. Following each chart will be a table showing the 7, 14, and 30 day projections for each model.

<br>

```{r fig.height = 5, fig.width = 10,echo=FALSE}

overlay = PlotOverlay(params$base, 
                      Counties, 
                      Hospitals, 
                      social_dist, 
                      params$pjDays,
                      "Hospitalizations")

overlay

```

<br>


<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">



<div class = "row">

<div class = "col-md-4">

<div class = "row">
<center>**7-Day Daily Hospitalization Projection**</center>
</div>


<div class = "row">


<div class = "col-md-6">

<center>IHME</center>

<center>`r (dplyr::filter(overlayDF7h, ID == "IHME"))[,2]`</center>

</div>


<div class = "col-md-6">

<center>CHIME</center>

<center>`r (dplyr::filter(overlayDF7h, ID == "CHIME"))[,2]`</center>

</div>

</div>


</div>




<div class = "col-md-4">

<div class = "row">
<center>**14-Day Daily Hospitalization Projection**</center>
</div>


<div class = "row">


<div class = "col-md-6">

<center>IHME</center>

<center>`r (dplyr::filter(overlayDF14h, ID == "IHME"))[,2]`</center>

</div>


<div class = "col-md-6">

<center>CHIME</center>

<center>`r (dplyr::filter(overlayDF14h, ID == "CHIME"))[,2]`</center>

</div>

</div>


</div>



<div class = "col-md-4">

<div class = "row">
<center>**30 Day Daily Hospitalization Projection**</center>
</div>


<div class = "row">


<div class = "col-md-6">

<center>IHME</center>

<center>`r (dplyr::filter(overlayDF30h, ID == "IHME"))[,2]`</center>

</div>


<div class = "col-md-6">

<center>CHIME</center>

<center>`r (dplyr::filter(overlayDF30h, ID == "CHIME"))[,2]`</center>

</div>

</div>


</div>



</div>
</div>


<br><br>

```{r fig.height = 5, fig.width = 9,echo=FALSE}

overlay = PlotOverlay(params$base, 
                      Counties, 
                      Hospitals, 
                      social_dist, 
                      params$pjDays,
                      "Deaths")
overlay
```


<br>


<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">



<div class = "row">

<div class = "col-md-4">

<div class = "row">
<center>**7-Day Total Fatality Projection**</center>
</div>


<div class = "row">


<div class = "col-md-6">

<center>IHME</center>

<center>`r (dplyr::filter(overlayDF7f, ID == "IHME"))[,2]`</center>

</div>


<div class = "col-md-6">

<center>CHIME</center>

<center>`r (dplyr::filter(overlayDF7f, ID == "CHIME"))[,2]`</center>

</div>

</div>


</div>




<div class = "col-md-4">

<div class = "row">
<center>**14-Day Total Fatality Projection**</center>
</div>


<div class = "row">


<div class = "col-md-6">

<center>IHME</center>

<center>`r (dplyr::filter(overlayDF14f, ID == "IHME"))[,2]`</center>

</div>


<div class = "col-md-6">

<center>CHIME</center>

<center>`r (dplyr::filter(overlayDF14f, ID == "CHIME"))[,2]`</center>

</div>

</div>


</div>



<div class = "col-md-4">

<div class = "row">
<center>**30 Day Total Fatality Projection**</center>
</div>


<div class = "row">


<div class = "col-md-6">

<center>IHME</center>

<center>`r (dplyr::filter(overlayDF30f, ID == "IHME"))[,2]`</center>

</div>


<div class = "col-md-6">

<center>CHIME</center>

<center>`r (dplyr::filter(overlayDF30f, ID == "CHIME"))[,2]`</center>

</div>

</div>


</div>



</div>
</div>


***
***


### Detailed County Info

This table displays information for each county within `r params$radius` miles of `r params$base`.


```{r echo=FALSE}
kable(CountyDT) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```


### `r params$base` Restriction ORM

**Cohort Demographics**

Col Header 1 | Col Header 2
------------ | ------------
Placeholder  | Pending move to FOUO

**Predicted Hospitilization Rate**

Col Header 1 | Col Header 2
------------ | ------------
Placeholder  | Pending move to FOUO
